\documentclass{article}
\usepackage{amsmath,amssymb,amstext,mathtools,array,url,bm,graphicx,color,epsfig}
\usepackage{fullpage,setspace}
\usepackage{authblk}
\usepackage{filecontents}
\usepackage{natbib}
\usepackage{lineno}
%\usepackage[colorlinks]{hyperref}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{float}
\usepackage[flushleft]{threeparttable}

\newtheorem{theorem}{Theorem}
\newtheorem{acknowledgement}[theorem]{Acknowledgement}
\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{axiom}[theorem]{Axiom}
\newtheorem{case}[theorem]{Case}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{conclusion}[theorem]{Conclusion}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{criterion}[theorem]{Criterion}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{solution}[theorem]{Solution}
\newtheorem{summary}[theorem]{Summary}
\newenvironment{proof}[1][Proof]{\noindent\textbf{#1.} }{\ \rule{0.5em}{0.5em}}

\begin{document}
\title{Probabilistic modeling and uncertainty quantification of the Atenquique debris flow, 1955, M\'exico}
\author[1,2]{Andrea Bevilacqua}
\author[3,1]{Abani Patra}
\author[2]{Marcus Bursik}
\author[4]{E. Bruce Pitman}
\author[3]{Ali Akhavan-Safaei}
\author[2]{David Hyman}
\author[5]{Jose Luis Mac\'ias}
\author[2]{Byron R. Rupp}
\author[6]{Ricardo Saucedo}

\affil[1]{\textit{Comp. Data Science and Eng., University at Buffalo, Buffalo, NY}}
\affil[2]{\textit{Dept. of Earth Sciences, University at Buffalo, Buffalo, NY} }
\affil[3]{\textit{Dept. of Mech. and  Aero. Eng., University at Buffalo, Buffalo, NY} }
\affil[4]{\textit{Dept. of Materials Design and Innovation, University at Buffalo, Buffalo, NY} }
\affil[5]{\textit{Dept. de Vulcanolog\'ia, Inst. de Geof\'isica, Universidad Nacional Aut\'onoma de M\'exico, Mexico City, MX} }
\affil[6]{\textit{Inst. de Geolog\'ia/Fac. Ingenier\'ia UASLP, San Luis Potos\'i, MX} }

\date{\texttt{\{abevilac\}@buffalo.edu}}


\maketitle
\abstract


\section{Introduction}


\section*{Acknowledgements}
We would like to acknowledge the support of NSF awards 1521855, 1621853, and 1339765.

\appendix


\bibliographystyle{apalike}
\bibliography{mybibfile}
\end{document}

